The fifteen year struggle of decentralizing privacy-enhancing technology

### 2014-03-26 paper.tex
Made OR1 / OR2 more readable in the section about Tor circuit creation

		Suppose Alice is an Onion Proxy that wants to connect through the Tor network to a web server. Circuit setup uses the Diffie-Hellman key-exchange protocol \cite{diffiehellman} to establish a shared secret between nodes. To create a new circuit, Alice first sends a \emph{create} cell with the first half of the Diffie-Hellman handshake to the first node in her selected path (for example, OR1). OR1 sends a \emph{created} cell back with the second half of the key along with a hash of the final key. Now both Alice and OR1 have a shared key they use to encrypt and decrypt data sent between them.

		So now Alice has a connection with the first Onion Router in the circuit. To extend the circuit to OR2, Alice first sends a \emph{relay extend} cell to OR1. This cell contains the address of the next Onion Router in the circuit and the first half of the key to use in the communication between her and OR2. OR1 takes this first half of the key and sends a \emph{create} cell with this key to OR2. When OR1 receives a created cell, OR1 passes this cell to Alice. Now Alice and OR2 share a common key. The same procedure can be used to extend the circuit with more nodes.

>>>>

		Suppose Alice is an Onion Proxy that wants to connect through the Tor network to a web server. Circuit setup uses the Diffie-Hellman key-exchange protocol \cite{diffiehellman} to establish a shared secret between nodes. To create a new circuit, Alice first sends a \emph{create} cell with the first half of the Diffie-Hellman handshake to the first node in her selected path (for example, $ OR_1 $). $ OR_1 $ sends a \emph{created} cell back with the second half of the key along with a hash of the final key. Now both Alice and $ OR_1 $ have a shared key they use to encrypt and decrypt data sent between them.

		So now Alice has a connection with the first Onion Router in the circuit. To extend the circuit to $ OR_2 $, Alice first sends a \emph{relay extend} cell to $ OR_1 $. This cell contains the address of the next Onion Router in the circuit and the first half of the key to use in the communication between her and OR2. $ OR_1 $ takes this first half of the key and sends a \emph{create} cell with this key to $ OR_2 $. When $ OR_1 $ receives a created cell, $ OR_1 $ passes this cell to Alice. Now Alice and $ OR_2 $ share a common key. The same procedure can be used to extend the circuit with more nodes.
